% Safety Info
\newcommand{\SYBRGOLD}{\item{\textbf{SYBR Gold} has no data available addressing the mutagenicity or toxicity of SYBR® Gold nucleic acid gel stain. Because this reagent binds to nucleic acids, it should be treated as a potential mutagen and handled with appropriate care. The DMSO stock solution should be handled with particular caution as DMSO is known to facilitate the entry of organic molecules into tissues.\cite{sybrGold}}}
\newcommand{\SYBRI}{\item{\textbf{SYBR Green I} is a mutagen and can penetrate laboratory gloves in a relatively short period of time, please change your gloves in the event of contamination. See \url{http://www.sigmaaldrich.com/MSDS/MSDS/DisplayMSDSPage.do?country=US&language=en&productNumber=S9430&brand=SIAL} for more information on the specifics of SYBR Green I. 
}}
\newcommand{\ETBR}{\item{\textbf{Ethidium Bromide} is a \textbf{serious mutagen} and is \textbf{significantly carcinogenic}. If working with considerable amounts, a \textbf{fume hood and respirator} are warranted. For more information see \url{https://www.sciencelab.com/msds.php?msdsId=9927667}
}}
\newcommand{\tdtSafety}{\item{\textbf{\tdt{}} is toxic if inhaled. May cause cancer. Toxic to aquatic life with long lasting effects. Avoid breathing dust/fume/gas/mist/vapours/spray. Use personal protective equipment as required. If Inhaled: Remove victim to fresh air and keep at rest in a position comfortable for breathing. Dispose of contents/container in accordance with local/regional/national/international regulations.\cite{Invitrogen2002}}}
\newcommand{\tdtBufferSafety}{\item{\textbf{\tdt{} Buffer} may cause cancer. It is also a skin irritant. However, ingestion/inhalation is not expected to present a significant ingestion hazard under anticipated conditions of normal use. If you feel unwell, seek medical advice.}}
